---
title: "PiaData"
author: "Bryan Milstead"
date: "Tuesday, February 17, 2015"
output: html_document
---
<!---
use these command instead of the knit icon if you want the data and work loaded into the R workspace
  library(knitr)
  setwd("~/PortableApps/R/scripts/Pia/Data")
  knit('PiaData.rmd')
-->
To Do
-------------------------
* Complete Bird List
* Complete Plant List

Work Notes
-------------------------
20150216
* Seno Pia split into Seno Pia Oeste and Seno Pia Este.  PBO is the only site in the west branch, the rest are in in Seno Pia Este.

20150217
* Harmonized lists between the mist nets and the counts.  Species captured in mistnet that weren't counted were added as zero values and vice versa for the mist net data.  This allows them to be plotted in the same order.

Introduction
-------------------------
* Bird Counts were conducted at sites on the Beagle Channel from Jan.21-31 2015.
* Mist netting was conducted at 3 sites during this period.

Data Processing
-------------------------
* read data from "DatosAvesPia.xls"
  - Counts: the raw count data
  - Obs: Observations on relative abundance by SiteCode, this table also contains the bird taxonmy and codes to be used throughout. Relative Abundance: 0=absent; 1=1-5 individuals; 2=6-20 individuals; 3=>20 individuals.
  - Sites: details on locations-this is joines to sites
  - PlantNames: plant taxonomy used

```{r getData, include=FALSE, echo=FALSE, cache=FALSE} 
  setwd("~/PortableApps/R/scripts/Pia/Data")
  library(RODBC)
  con<-odbcConnectExcel("DatosAvesPia.xls") # open a connection to the Excel file
  sqlTables(con)$TABLE_NAME # get list of all sheets
  Counts<-sqlFetch(con, 'Counts$',stringsAsFactors=FALSE) # read a sheet
  Obs<-sqlFetch(con, 'Observations',stringsAsFactors=FALSE) # read a sheet
  Sites<-sqlFetch(con, 'Sites',stringsAsFactors=FALSE) # read a sheet
  plantNames<-sqlFetch(con, 'PlantNames',stringsAsFactors=FALSE) # read a sheet
  mist<-sqlFetch(con, 'MistNets',stringsAsFactors=FALSE) # read a sheet
  close(con)
#select plant and bird columns
  names(Counts)
  BC<-11:31
  PC<-32:48
```
  
* add the Site information to Counts

```{r Sites, include=FALSE, echo=FALSE, cache=FALSE} 
  #add site information to Counts
    #Check that all SiteCodes in Obs and Counts match "Sites"
      table(unique(Counts$SiteCode)%in%unique(Sites$SiteCode))
    #add Sites to Counts
      Counts<-merge(Counts,Sites[,-5],by='SiteCode',all.x=T)
```

* Aggregate Bird and Plant Counts by Area

```{r Aggregate, include=FALSE, echo=FALSE, cache=FALSE}   
  #function to aggregate relative abundance (birds) or percent present (Plants) by site or area
    Sitio<-function(Sp,Aggregator){
      x<-Counts[,Sp]
      #StdErr function
        se<-function(x) sd(na.exclude(x))/sqrt(length(na.exclude(x)))
      #Length na.rm function
        len<-function(x) length(na.exclude(x))
      #get N
      Out<-aggregate(x,by=list(Aggregator),len)
      names(Out)<-c('SiteCode','N')
      #get mean
      Mean<-aggregate(x,by=list(Aggregator),mean,na.rm=TRUE)
      names(Mean)<-c('SiteCode','Mean')
      Out$Mean<-Mean$Mean
      #get SE
      SE<-aggregate(x,by=list(Aggregator),se)
      names(SE)<-c('SiteCode','StdErr')
      Out$StdErr<-SE$StdErr
      #Add Species
      Out$Sp<-Sp
      #round mean & StdErr
        Out$Mean<-round(Out$Mean,2)
        Out$StdErr<-round(Out$StdErr,2)
      return(Out)
    }
    

#birds
  #Loop to aggregate all birds by Area
    a<-names(Counts)[BC]
  #start loop
    areaBirds<-c()
    for(i in c(1:length(a)) ){
      x<-Sitio(a[i],Counts$Area)
      areaBirds<-rbind(areaBirds,x)
    }
    names(areaBirds)[c(1,5)]<-c('Area','Abbr')
  #add taxonomy
    areaBirds<-merge(areaBirds,Obs[,3:7],by='Abbr',all.x=T)

#plant data
  #Loop to aggregate all plants by area
    a<-names(Counts)[PC]
  #start loop
    areaPlants<-c()
    for(i in c(1:length(a)) ){
      x<-Sitio(a[i],Counts$Area)
      areaPlants<-rbind(areaPlants,x)
    }
    names(areaPlants)[1]<-'Area'
  #add taxonomy
    areaPlants<-merge(areaPlants,plantNames,by.x='Sp',by.y='ColumnName',all.x=TRUE)
```  

* standardize the mistnet data

```{r Mist, include=FALSE, echo=FALSE, cache=FALSE}  
  mist$IndividualsAdj<-round(10000*mist$Individuals/(mist$EffortHours*mist$NetAreaM2),2)
```

* Save the data to PiaData.rda

```{r Save, include=FALSE, echo=FALSE, cache=FALSE}  
  save(Counts,Obs,mist,areaBirds,areaPlants,file='PiaData.rda') 
```  


