---
title: "Analysis"
author: "Bryan Milstead"
date: "Tuesday, February 17, 2015"
output: html_document
---
<!---
use these command instead of the knit icon if you want the data and work loaded into the R workspace
  library(knitr)
  setwd("~/PortableApps/R/scripts/Pia/")
  knit('R/Analysis.rmd')
-->
To Do
-------------------------
* 

Work Notes
-------------------------
201502??
* 

Introduction
-------------------------
* Bird Counts were conducted at sites on the Beagle Channel from Jan.21-31 2015.
* Mist netting was conducted at 3 sites during this period.

Analysis
----------------
* Load data

```{r setup, include=FALSE, echo=FALSE, cache=FALSE} 
  load('Data/PiaData.rda') 
```

* Plot Bird counts by area

```{r setup, include=FALSE, echo=FALSE, cache=FALSE} 
  #plotOrder for each species determined by means
    a<-aggregate(areaBirds$Mean,by=list(areaBirds$Abbr),mean)
    a<-a[order(a$x,decreasing=TRUE),]
    a$plotOrder<-1:nrow(a)
    a<-a[,-2]
    names(a)<-c('Abbr','plotOrder')

  #add plotOrder to Birds and sort
    areaBirds<-merge(areaBirds,a,by='Abbr',all.x=TRUE)
    areaBirds<-areaBirds[order(c(areaBirds$plotOrder)),]
  

  #plot birds by area
    #function to make plots
      plotArea<-function(Area='Seno Alemania',Xlab=FALSE){
        Sp<-areaBirds[areaBirds$Area==Area,]
        if(Xlab==TRUE) {
          #xlabels<-substr(unique(Sp$Abbr),1,4)
          xlabels<-unique(Sp$Abbr)
        }else{
          xlabels<-NULL}
        Legend<-paste(unique(Sp$Area),' (N=',unique(Sp$N),")",sep='')
        x<-barplot(Sp$Mean,ylim=c(0,max(areaBirds$Mean+areaBirds$StdEr+.1)),names.arg=xlabels,axes=FALSE,cex.names=1.75,las=2)
        arrows(x,Sp$Mean-Sp$StdErr,x,Sp$Mean+Sp$StdErr,code=3,angle=90,length=.1)
        box()
        text(15,2,Legend,cex=2,adj=0)
        axis(2,at=1:2,labels=TRUE,las=1.5,cex.axis=2)
      }

###########setup for a multipanel graph
  Mai<-c(0,1,0.0000,0.1)  #default=c(1.36,1.093,1.093,0.56)
  Omi<-c(1.2,0.0,0.25,0.5)     #default=c(0,0,0,0)
  win.graph(11, 8.5) 
  par(mfrow=c(6,1),mai=Mai,omi=Omi)
  plotArea("Seno Alemania",FALSE)
  plotArea("Seno Torcido",FALSE)
  plotArea("Seno Holanda",FALSE)
  plotArea("Isla Hoste",FALSE)
    mtext("          Mean Abundance / Station (+/- StdErr)",2,4,cex=1.75)
  plotArea("Seno Pia Oeste",FALSE)
  plotArea("Seno Pia Este",TRUE)
    #mtext("Species",1,4,cex=2)
  
      

  
  
  barplot(Sp$Mean,names.arg=unique(Sp$Abbr),axes=FALSE,cex.names=.7,las=1.5)
  axis(2,at=1:2,labels=TRUE,las=1.5,cex.axis=2)
  
  ###########old
  
  
#plot birds by area
  a<-unique(Birds$Area)
  i<-1
  Sp<-Birds[Birds$Area==a[i],]
  xlabels=Sp$Abbr
  x<-barplot(Sp$Mean,ylim=c(0,max(areaBirds$Mean+areaBirds$StdEr+.1)),names.arg=xlabels,axes=FALSE)
  arrows(x,Sp$Mean-Sp$StdErr,x,Sp$Mean+Sp$StdErr,code=3,angle=90,length=.1)
  box()
  text(.25,2.4,unique(Sp$Area),cex=2,adj=0)
  axis(2,at=1:2,labels=TRUE,las=1.5)
  
  
  
  
  

#Plot Sp by Area
  
plotAggr<-function(Aggr=Birds$Abbr,i=11){
  a<-unique(Aggr)
  Sp<-Birds[Birds$Abbr==a[i],]
  xlabels=Sp$Area
  x<-barplot(Sp$Mean,ylim=c(0,max(areaBirds$Mean+areaBirds$StdEr+.1)),names.arg=xlabels,axes=FALSE)
  arrows(x,Sp$Mean-Sp$StdErr,x,Sp$Mean+Sp$StdErr,code=3,angle=90,length=.1)
  box()
  text(.25,2.4,unique(Sp$EnglishName),cex=2,adj=0)
  axis(2,at=1:2,labels=TRUE,las=1.5)
}
  
  #windows(10,7.5)
  plotAggr(Aggr=Birds$Abbr,15)
  
  
  Aggr=Birds$Area
  i=1
    a<-unique(Aggr)
    Sp<-Birds[Birds$Abbr==a[i],]
    xlabels=Sp$Abbr
    x<-barplot(Sp$Mean,ylim=c(0,max(areaBirds$Mean+areaBirds$StdEr+.1)),names.arg=xlabels,axes=FALSE)
    arrows(x,Sp$Mean-Sp$StdErr,x,Sp$Mean+Sp$StdErr,code=3,angle=90,length=.1)
    box()
    text(.25,2.4,unique(Sp$EnglishName),cex=2,adj=0)
    axis(2,at=1:2,labels=TRUE,las=1.5)
  }
  
  
  
  x<-barplot(Sp$Mean,ylim=c(0,max(areaBirds$Mean+areaBirds$StdEr)),names.arg=Sp$Area, ylab="Relative Abundance (+/- 1 stdErr)",xlab='Site')
  
  text(.75,2.4,'xxxxxxxxxxxxxxx',cex=2,adj=0)

